A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-04 tex/codatadp.tex
more ideas

  * codatatypes: from a theoretical and implementational point of view, like
      datatypes but:
    * codatatypes are never empty (e.g. finite streams are rejected)

>>>>

  * codatatypes: from a theoretical and implementational point of view, like
      datatypes but:
    * infinite values (infinitely many nested constructors)
    * codatatypes are never empty (e.g. finite streams are rejected)
